### 2014-11-12 minimax.tex
spacing
rewording, spacing

The algorithm proceeds by building a game tree, where each tree node represents a
game state and the children represent the possible game moves that can
be made by either player 1 or player 2.
An evaluation function is used to compute the score of
the board for each leaf of the tree. A node is a leaf when the game state can no longer be
expanded. Finally, the
algorithm recursively minimizes or maximizes the scores of each node.
To select the best move for player 1, the
algorithm picks the move maximized at the root node.

@@

expand(A, Board, [C | Xs], N, P, \underline{Depth})
C <> 0
  -o expand(A, Board ++ [C], Xs, N, P, \underline{Depth}).
\end{Verbatim}
\scap{minimax:check-end}{MiniMax: checking if the game has ended and expanding the tree}
\end{topfig}
\normalsize

@@

\begin{topfig}
\vspace*{-2ex}
   \begin{center}
      \subfloat[]{\small\begin{tabular}[b]{ | c | c | c |}
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 11.80GB & 0.50MB \\ \hline
         2 & 12.19GB & 1.45MB \\ \hline
         4 & 13.82GB & 2.35MB \\ \hline
         8 & 14.87GB & 4.36MB \\ \hline
         16 & 13.79GB & 8.1MB \\ \hline
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=4.5cm]{results/min-max-tictactoe.png}}
   \end{center}
   \scap{results:memory_minmax}{Memory usage and scalability of the regular and coordinated versions
      of MiniMax.}
\end{topfig}

>>>>

The algorithm builds a game tree, where each tree node represents a
game state and the children represent the possible game moves that can
be made by either player 1 or player 2.  An evaluation function is
used to compute the score of the board for each leaf of the tree. A
node is a leaf when the game state can no longer be expanded. Finally,
the algorithm recursively minimizes or maximizes the scores of each
node.  To select the best move for player 1, the algorithm picks the
move maximized at the root node.

@@

expand(A, Board, [C | Xs], N, P, \underline{Depth})
C <> 0
  -o expand(A, Board ++ [C], Xs, N, P, \underline{Depth}).
\end{Verbatim}
\scap{minimax:check-end}{MiniMax: checking if the game has ended and expanding the tree}
\vspace*{-2ex}
\end{topfig}
\normalsize

@@

\begin{topfig}
\vspace*{-3ex}
   \begin{center}
      \subfloat[]{\small\begin{tabular}[b]{ | c | c | c |}
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 11.80GB & 0.50MB \\ \hline
         2 & 12.19GB & 1.45MB \\ \hline
         4 & 13.82GB & 2.35MB \\ \hline
         8 & 14.87GB & 4.36MB \\ \hline
         16 & 13.79GB & 8.1MB \\ \hline
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=4.5cm]{results/min-max-tictactoe.png}}
   \end{center}
   \scap{results:memory_minmax}{Memory usage and scalability of the regular and coordinated versions
      of MiniMax.}
\vspace*{-2ex}
\end{topfig}
